\documentclass[a4paper,12pt]{article}

\begin{document}

\section*{Task 1}

For the first task we will have the user create a new account for the first time. The app will be ``running'' and
at the log in page, the only information that will be proivded to the user is that they do not have account in the
app, and if nessesary will tell them to create a new account. At this point they should sellect the sign up button.
This will take them to a new view that will collect information from the user such as name, master password, etc.


\section*{Task 2}
At this point the user should not have any passwords in the account, the next task should get the user to add
a password to the account. We will assume that the user is on the main page with no accounts in the left
sidebar. From the main page the user will select the plus icon in the top left hand corn. This will cause
the new account overlay to pop up. For the purpose of the test the user will not be selecting a logo for
the account and thus keep the default logo. If the user selects the add logo button, we will report to
the user that the device is new and there are no aviable picutres to use $($or something like that$)$.
For this test we will have the user create a google account. Once the user fills in the add button
the overlay will close and return to the main page. At this point we will see a new entry in the
account list. The user will then log out of the app.

\section*{Task 3}

For this task the user will back at the login page. They will proceed to log into the app and go to the 
main page, at this point we will use one of the views that some more websites populated in the account.
This will include groups but at this time users will not be able to create/edit/remove groups. We will
have the users log into a couple of apps, in this case Google and Twitter. 

\end{document}
